### 2020-01-14 ISSTA/introduction.tex
contribs

Previous practical approaches to
nondeterminism/flaky test detection and debugging rely either on 1) identifying
potential sources of nondeterminism such as test inter-dependence
\cite{LamZE2015} or certain code smells \cite{palomba2017does}  or 2)
use a heuristic approach to mark failures as likely flaky, such as that taken by DeFlaker
\cite{bell2018d}.  In the real world, people usually detect flaky
tests by the most obvious heuristic of all:  they observe a test both
fail and pass for the same code version.  In a sense, even DeFlaker
relies on this method, but avoids having to observe a flaky test actually
passing, by inferring that if a test was previously passing, and
executes no changed code, its failure after a code change \emph{must}
be due to flakiness/nondeterminism.  Our approach to the problem is
fundamentally different, and essentially orthogonal; we concentrate on the detection and avoidance of
nondeterminism/flakiness using \emph{automated test generation},
and make it possible for a developer or test engineer to detect when
important values generated in automated testing differ without a
change in the test itself or the code under test.  While some of these
changes may be harmless, and unable to propagate to cause test
failures, they are potential sources of flaky behavior.  To our
knowledge, this is the first approach to the problem that
allows detection of (potential sources of) flakiness, based on real divergence in
behavior, without having to observe a test actually fail due to nondeterminism.

This approach enables a number of useful results:
 the automated production of
nondeterminism-free regression tests even for libraries with some
sources of nondeterminism, the documentation of sources of
nondeterminism that might produce problems for manually-constructed
tests, and, most importantly, detection and \emph{effective debugging}
(using a novel modification of delta-debugging designed for
nondeterminism) for
unexpected nondeterminism that is, itself, a bug.  Additonally, by
identifying library behaviors that are
nondeterministic, our approach should make it much easier to flag
statements in existing human-written unit tests that may produce flaky
behavior:  simply scan the
code for calls to such functions.  We use a set
of case studies. including real-world, widely-used, Python libraries to demonstrate the
utility of our ideas.  Failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.

>>>>

Previous practical approaches to
nondeterminism/flaky test detection and debugging rely either on 1) identifying
potential sources of nondeterminism such as test inter-dependence
\cite{LamZE2015} or certain code smells \cite{palomba2017does}  or 2)
use a heuristic approach to mark failures as likely flaky, such as that taken by DeFlaker
\cite{bell2018d}.  In the real world, people usually detect flaky
tests by the most obvious heuristic of all:  they observe a test both
fail and pass for the same code version.  In a sense, even DeFlaker
relies on this method, but avoids having to observe a flaky test actually
passing, by inferring that if a test was previously passing, and
executes no changed code, its failure after a code change \emph{must}
be due to flakiness/nondeterminism.  Our approach to the problem is
fundamentally different, and essentially orthogonal; we concentrate on the detection and avoidance of
nondeterminism/flakiness using \emph{automated test generation},
and make it possible for a developer or test engineer to detect when
important values generated in automated testing differ without a
change in the test itself or the code under test.  While some of these
changes may be harmless, and unable to propagate to cause test
failures, they are potential sources of flaky behavior.  To our
knowledge, this is the first approach to the problem that
allows detection of (potential sources of) flakiness, based on real divergence in
behavior, without having to observe a test actually fail due to nondeterminism.  we additionally introduce the first variation of delta-debugging that properly handles probabilistic faults and reduction properties.

Our methods enable automated production of
nondeterminism-free regression tests even for libraries with some
sources of nondeterminism, documentation of sources of
nondeterminism that might produce problems for manually-constructed
tests, and, most importantly, detection of 
unexpected nondeterminism that is, itself, a bug.  We use a set
of case studies. including real-world, widely-used, Python libraries, to demonstrate the
utility of our ideas.  Our novel notion of failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.
